Read quality check

### 2019-02-11 scripts/qual-check.Rmd
REstructure to Snakemake standard, part 2 (actual restructuring)

```{r eval = FALSE}
counts <- read_csv(file.path(data.dir, "fastq.counts"), col_names = c("file", "reads"))
counts %<>% mutate(dataset = map(file, str_extract, datasets$Dataset) %>%
                     map_chr(purrr::compose(dplyr::first, sort, unique)),
                   seq.run = map(file, str_extract, datasets$Seq.Run) %>%
                     map_chr(purrr::compose(dplyr::first, sort, unique)),
                   well = str_extract(file, "[A-H]\\d\\d?"),
                   shard = str_extract(file, "\\bx[a-z][a-z]\\b"),
                   is.shard = !is.na(shard),
                   region = str_extract(file, "(ITS[12]|LSU)"),
                   is.trim = str_detect(file, "trim"),
                   is.demux = is.na(region) & !is.trim & !is.na(well),
                   type = ifelse(is.trim, "trim",
                                 ifelse(!is.na(region), "ITSx",
                                        ifelse(is.demux, "demux",
                                               "original"))),
                   plate = str_extract(file, "00\\d") %>% replace_na("001")) %>%
  group_by(dataset, type, plate, region, is.shard) %>%
  summarize(reads = sum(reads)) %>%
  ungroup() %>%
  select(-is.shard) %>%
  unique() %>%
  spread(key = "type", value = "reads") %>%
  select(dataset, plate, original, demux, region, ITSx, trim) %>%
  filter(!is.na(dataset)) %>%
  group_by(dataset) %>%
  mutate(original = na.omit(original),
         demux = na.omit(demux)) %>%
  filter(all(is.na(region)) | !is.na(region)) %>%
  ungroup()

>>>>

```{r eval = FALSE}
counts <- readd(seq_counts) %>% 
  tidyr::extract(col = "file",
                     into = c("Seq.Run", "Plate", "Well","Region","Type"),
                     regex = "([:alpha:]+_\\d+)_(\\d+)-([A-H]1?\\d)[fr]?-?([:alnum:]*)\\.([:alnum:]+).+") %>%
  mutate(Type = ifelse(Type == "trim" & str_length(Region) > 0,
                       "itsx",
                       Type)) %>%
  group_by(Seq.Run, Region, Type) %>%
  summarize(reads = sum(reads)) %>%
  spread(key = "Type", value = "reads") %>%
  select(Seq.Run, trim, Region, itsx, qfilt) %>%
  group_by(Seq.Run) %>%
  mutate(trim = na.omit(trim)) %>%
  filter(all(is.na(itsx)) | !is.na(itsx)) %>%
  ungroup()
